### 2020-04-21 dataprep.tex
minor comments
added side view

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Data Collection and Preprocessing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data Collection and Preprocessing}
\label{section:dataprep}
Data on GPU life times is constructed from two sources: inventory runs
and failure event records. Two types of failure events were collected:
Double Bit Error (DBE) and Off the Bus (OTB). DBE was found to be the
``signature'' error of eventual GPU failures and a trigger for their
replacement.

@@

The location references are cabinet column (0-24), row (0-7), cage
(0-3), slot (0-7), and node (0-3) with respect to the layout shown in
Figure~\ref{fig:layout}.
\begin{figure}
  \centering
  \begin{minipage}{0.49\columnwidth}
    \includegraphics[width=\columnwidth]{figs/TitanCabinet.png}
  \end{minipage}
  \begin{minipage}{0.49\columnwidth}
    \includegraphics[width=\columnwidth]{figs/TitanBlade.png}

    \vspace{5em}
    \includegraphics[width=\columnwidth]{figs/TitanLayout.png}
  \end{minipage}
  \caption{Titan cabinet, blade, and floor layout. Cooling airflow is
    bottom to top within a cabinet, taking ambient air in at the foot
    and relasing it back out at the top. Cooling fluid is passed
    through two heat exchangers, one below Cage 0 and one above Cage
    2.}
  \label{fig:layout}
\end{figure}

>>>>

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Data Collection and Preprocessing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data Collection and Preprocessing}
\label{section:dataprep}
Data on GPU life times is constructed from two sources: inventory runs
and failure event records. Two types of failure events were collected:
Double Bit Error (DBE) and Off the Bus (OTB). DBE was found to be the
``signature'' error of eventual GPU failures and a trigger for their
replacement. \fix{RA: Should we point out that this replacement was only done later on?}

@@

The location references are cabinet column (0-24), row (0-7), cage
(0-3), slot (0-7), and node (0-3) with respect to the layout shown in
Figure~\ref{fig:layout}.
\begin{figure}
  \centering
  \begin{minipage}{0.49\columnwidth}
    \includegraphics[width=\columnwidth]{figs/TitanCabinet.png}
    \includegraphics[width=0.9\columnwidth]{figs/TitanCabinetSide.png}
  \end{minipage}
  \begin{minipage}{0.49\columnwidth}
    \includegraphics[width=\columnwidth]{figs/TitanBlade.png}

    \vspace{0.8\columnwidth}
    \includegraphics[width=\columnwidth]{figs/TitanLayout.png}
  \end{minipage}
  \caption{Titan cabinet (front view and side view with air flow) on
    the left, blade layout and floor layout on the right. Cooling
    airflow is bottom to top within a cabinet, taking ambient air in
    at the foot and relasing it back out at the top. Cooling fluid is
    passed through two heat exchange evaporators, one below Cage 0 and
    one above Cage 2.}
  \label{fig:layout}
\end{figure}

### 2020-04-21 survival.tex
added side view

Kaplan-Meier survival analysis (KM) gives the probability of survival
beyond a given time. It is a nonparametric technique that makes no
specific failure model assumptions, such as Weibull, Exponential,
etc. The technique is able to use censored observations and can also
split the data into subpopulations and compute separate survival
curves.

If $T$ is taken to be the random variable of a GPU fail time, then its
probability density function is $f(t)$ and its cumulative distribution
function $F(t) = Pr\{T < t\}$ gives the probability that a GPU fails
by duration $t$. The survival function is then 
\begin{displaymath}
  S(t) = Pr\{T \geq t\} = 1 - F(t) = \int_t^\infty f(x)dx,
\end{displaymath}
which is the probability of being operational at duration $t$.  We use
the R packages \pkg{survival} and \pkg{survminer} for the KM analysis,
which is reported in Figure~\ref{fig:km-all-cage-node}. Within each
batch, separate survival curves are computed for each cage by node
combination.

>>>>

Kaplan-Meier survival analysis (KM) gives the probability of survival
beyond a given time. It is a nonparametric technique that makes no
specific failure model assumptions, such as Weibull, Exponential,
etc. The technique is able to use censored observations and can also
split the data into subpopulations to compute separate survival
curves.

If $T$ is taken to be the random variable of a GPU fail time, then its
probability density function is $f(t)$ and its cumulative distribution
function $F(t) = Pr\{T < t\}$ gives the probability that a GPU fails
by duration $t$. The survival function is then its complement
\begin{displaymath}
  S(t) = Pr\{T \geq t\} = 1 - F(t) = \int_t^\infty f(x)dx.
\end{displaymath}
It is the probability of being operational at duration $t$.  We use
the R packages \pkg{survival} and \pkg{survminer} for the KM analysis,
which is reported in Figure~\ref{fig:km-all-cage-node}. Within each
batch, separate survival curves are computed for each cage by node
combination.
